Efficient Coalition Formation for Web Services

### 2013-03-02 papers/coalition/coalition.tex
Changes

*** on functional and non-functional requirements specially for critial applications
*** on community of web services

@@

@@

@@

>>>>

\\ *** on functional and non-functional requirements specially for critial applications

\\ *** on community of web services

\cite{DBLP:conf/IEEEscc/KhosravifarABT11}
\cite{DBLP:conf/IEEEscc/LimTMB12}

@@

\subsubsection{Shapley value}

@@

\subsubsection{Core}

@@

\subsubsection{Coalition Structure Formation}

Coalition structure formation is the problem of finding best partition of agents into teams, focusing more on optimizing the coalition's ``owner'' payoff. In these settings performance of individual agent is less important than the $social welfare$ of the system, which is the sum of the values of all teams. Having characterestic function game G, a coalition structure (CS) is $socially optimal$ is CS belongs to set $argmax_{CS \in CS_N}v(CS)$ where v(CS) is sum of the total valuation function of all coalitions inside CS $(v(CS) = \sum_{C \in CS_N}v(CS))$.
